\Large \bf Relationship of Weather and Maize Yields in Kenya

### 2018-11-14 writing/draft1/draftMonika3.tex
adding

\begin{itemize}
\item Seasonal cumulative rainfall
\item Seasonal standard deviation 
\item Seasonal coefficient of variation 
\item Maximum length of dry spell in number of days
\item ...\textcolor{blue}{the list to be finished}
\item...
\end{itemize}
\item Temperature
\begin{itemize}
\item
\item\textcolor{blue}{the list to be finished}..
\item
\end{itemize}
\end{itemize}
\subsection{Data}
\textcolor{blue}{source of data, resolution and plots/barplots of yield, precip and temp when final data available.}\\
\textcolor{red}{maybe a table of descriptive statistics or ref to the tale to appendix}
\textcolor{blue}{also how the weather data were aggregated spatially over counties}
\subsection{Linear mixed models}
\sloppy
Kenya consists of $47$ counties with semi-autonomous county governments  \citep{Barasa2017}. As a result of the high degree of county-level autonomy, the policies and regulations often differ across the counties, hence the effects of weather on crop yield are likely to be different across the counties. Therefore, following the standard methodology, we estimated a battery of linear mixed effects models (mixed models) commonly used to analyse longitudinal data \citep{bates2000mixed}. Mixed models are suitable for analysis of panel data as they account for the panel structure of the dataset. These types of models include both fixed affects and random effects. Fixed effects are analogous to parameters in a classical linear regression model and value of each effect is assumed to be fixed over all counties \citep{bates2010lme4}. On the other hand, random effect are unobserved random variables. There are at least three benefits of treating a set of parameters as a random sample from some distribution. \textit{(i)} Extrapolation of inference to a wider population \textit{(ii)} improved accounting for system uncertainty and \textit{(iii)} efficiency of estimation (\citealp{KERYch9,KERYch12}).

@@

  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}  &\multicolumn{1}{c}{\textit{Estimate}} &\multicolumn{1}{c}{\textit{p-value}}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.158$&$0.086^{\bullet}$\\
  \\
\vspace{-0.2cm}Prec. cum. MAM+OND lag 1, east&$0.066$&$0.008^{**}$\\
  \\
  \vspace{-0.2cm}Prec. cum. MAM lag 1, west&$-0.006$&$0.861$\\
  \\
  \vspace{-0.2cm}Temp. avg. Mar.-Sep. lag 1, east&$-0.036$&$0.292$\\
  \\
    \vspace{-0.2cm}Temp. avg. Mar.-Sep. lag 1, west&$-0.081$&$0.008^{**}$\\
  \\

      \vspace{-0.2cm}Prec. max OND, east&$0.081$&$0.056^{\bullet}$\\
  \\
        \vspace{-0.2cm}Prec. max OND, west&$0.108$&$0.009^{**}$\\
  \\
    \vspace{-0.2cm}Temp. sd. Oc.-Mar. lag 1, east&$0.101$&$0.003^{**}$\\
  \\
      \vspace{-0.2cm}Temp. sd. Oc.-Mar. lag 1, west&$0.142$&$6\times10^{-7}$ $^{***}$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \\
  \vspace{-0.2cm}Prec. cum. MAM+OND lag 1\\
  \\
  \vspace{-0.2cm}Prec. max OND\\
  \\
    \vspace{-0.2cm}Temp. avg. Mar.-Sep. lag 1\\
  \vspace{-0.1cm} \\ 
  \hline

\end{tabular} 
\end{small}
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} \hspace{0.05cm}$584$ observations
        \begin{adjustwidth}{1cm}{} 
    \item \hspace{0.45cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
     \end{adjustwidth}
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\linespread{1}

>>>>

\begin{itemize}
\item Seasonal cumulative rainfall
\item Seasonal standard deviation 
\item Seasonal coefficient of variation 
\item Maximum length of dry spell in number of days
\item ...\textcolor{blue}{the list to be finished}
\item...
\end{itemize}
\item Temperature
\begin{itemize}
\item
\item\textcolor{blue}{the list to be finished}..
\item
\end{itemize}
\end{itemize}
\subsection{Data}
\textcolor{blue}{source of data, resolution and plots/barplots of yield, precip and temp when final data available.}\\
\textcolor{red}{maybe a table of descriptive statistics or ref to the tale to appendix}
\textcolor{blue}{also how the weather data were aggregated spatially over counties}
\subsection{Linear mixed models}
\sloppy
Kenya consists of $47$ counties with semi-autonomous county governments  \citep{Barasa2017}. As a result of the high degree of county-level autonomy, the policies and regulations often differ across the counties, hence the effects of weather on crop yield are likely to be different across the counties. Therefore, following the standard methodology, we estimated a battery of linear mixed effects models (mixed models) commonly used to analyse longitudinal data \citep{bates2000mixed}. Mixed models are suitable for analysis of panel data as they account for the panel structure of the dataset. These types of models include both fixed effects parameters and random effects. Fixed effects are analogous to parameters in a classical linear regression model and value of each effect is assumed to be fixed over all counties \citep{bates2010lme4}. On the other hand, random effect are unobserved random variables. There are at least three benefits of treating a set of parameters as a random sample from some distribution. \textit{(i)} Extrapolation of inference to a wider population \textit{(ii)} improved accounting for system uncertainty and \textit{(iii)} efficiency of estimation (\citealp{KERYch9, KERYch12}).

@@

  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}  &\multicolumn{1}{c}{\textit{Estimate}} &\multicolumn{1}{c}{\textit{p-value}}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.158$&$0.086^{\bullet}$\\
  \\
\vspace{-0.2cm}Precipitation total&$0.066$&$0.008^{**}$\\
  \\
  \vspace{-0.2cm}Precipitation total sq.&$-0.006$&$0.861$\\
  \\
  \vspace{-0.2cm}Temperature - average&$-0.036$&$0.292$\\
  \\
    \vspace{-0.2cm}Precipitation $\times$ temperature& $-0.081$&$0.008^{**}$\\
  \\

      \vspace{-0.2cm}Prec. c. of variation&$0.081$&$0.056^{\bullet}$\\
  \\
        \vspace{-0.2cm}Temp. std. d.&$0.108$&$0.009^{**}$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \hline
\\
\end{tabular} 
\end{small}
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} \hspace{0.05cm}$584$ observations
        \begin{adjustwidth}{1cm}{} 
    \item \hspace{0.45cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
     \end{adjustwidth}
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\linespread{1}

### 2018-11-14 writing/draft1/draftMonika4.tex
adding

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{caption}
\usepackage{array}
\usepackage{pdfpages}
\usepackage{float}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{amsxtra}
\usepackage{amsbsy}
\usepackage{bm}
\usepackage{accents}
\usepackage{chngcntr}
\usepackage{dcolumn}
\usepackage[none]{hyphenat}
\usepackage[affil-it]{authblk}
\usepackage{datetime}
\usepackage{colortbl}
\usepackage{footnote}
\makesavenoteenv{tabular}
\usepackage[flushleft]{threeparttable}
\usepackage[hyphens]{url}
\usepackage{placeins}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{changepage}  
\usepackage{mathrsfs}

@@

{\centering
\begin{threeparttable}

\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather}}
% Peggy45ln can be found in foodSystems/Rcodes/Lags/..
 % Yield in tonnes per hectare
\label{Peggy45ln} 
\centering
\begin{small}
\begin{tabular}{lrl} 
\hline \vspace{-0.2cm} \\

@@

  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}  &\multicolumn{1}{c}{\textit{Estimate}} &\multicolumn{1}{c}{\textit{p-value}}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.158$&$0.086^{\bullet}$\\
  \\
\vspace{-0.2cm}Precipitation total&$0.066$&$0.008^{**}$\\
  \\
  \vspace{-0.2cm}Precipitation total sq.&$-0.006$&$0.861$\\
  \\
  \vspace{-0.2cm}Temperature - average&$-0.036$&$0.292$\\
  \\
    \vspace{-0.2cm}Precipitation $\times$ temperature& $-0.081$&$0.008^{**}$\\
  \\

      \vspace{-0.2cm}Prec. c. of variation&$0.081$&$0.056^{\bullet}$\\
  \\
        \vspace{-0.2cm}Temp. std. d.&$0.108$&$0.009^{**}$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \hline
\\
\end{tabular} 
\end{small}
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} \hspace{0.05cm}$584$ observations
        \begin{adjustwidth}{1cm}{} 
    \item \hspace{0.45cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
     \end{adjustwidth}
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\linespread{1}

>>>>

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{caption}
\usepackage{array}
\usepackage{pdfpages}
\usepackage{float}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{amsxtra}
\usepackage{amsbsy}
\usepackage{bm}
\usepackage{accents}
\usepackage{chngcntr}
\usepackage{dcolumn}
\usepackage[none]{hyphenat}
\usepackage[affil-it]{authblk}
\usepackage{datetime}
\usepackage{colortbl}
\usepackage{footnote}
\makesavenoteenv{tabular}
\usepackage[flushleft]{threeparttable}
\usepackage[hyphens]{url}
\usepackage{placeins}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{changepage}  
\usepackage{mathrsfs}
\usepackage{gensymb}

@@

{\centering
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(0,0) errors}}
% AmBEST00, AmBEST, AmBEST99
\label{Models1} 
\centering
\begin{small}
\begin{tabular}{lccc} 
\hline \vspace{-0.2cm} \\

@@

  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}  &\multicolumn{1}{c}{\textit{Model 1}} &\multicolumn{1}{c}{\textit{Model 2}} &\multicolumn{1}{c}{\textit{Model 3}}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.298$ $(0.066)^{***}$&$0.256$ $(0.061)^{***}$&$0.243$ $(0.076)^{**}$\\
  \\
\vspace{-0.2cm}Precipitation total&$0.289$ $(0.045)^{***}$&$0.131$ $(0.046)^{**}$&$0.137$ $(0.125)^{}$\\
  \\
  \vspace{-0.2cm}Precipitation total sq.&$-0.071$ $(0.028)^{*}$&$-0.075$ $(0.026)^{**}$&$-0.073$ $(0.039)^{\bullet}$\\
  \\
  \vspace{-0.2cm}Temperature - average&$-0.202$ $(0.062)^{**}$&$-0.188$ $(0.058)^{**}$&$-0.464$ $(0.144)^{**}$\\
  \\
    \vspace{-0.2cm}Precip. $\times$ temperature&---&$-0.135$ $(0.037)^{***}$&$-0.108$ $(0.051)^{*}$\\
  \\
      \vspace{-0.2cm}Prec. c. of variation&---&$-0.198$ $(0.035)^{***}$&$-0.181$ $(0.075)^{*}$\\
  \\
        \vspace{-0.2cm}Temp. std. dev.&---&$0.064$ $(0.021)^{**}$&$0.058$ $(0.027)^{*}$\\
  \\
          \vspace{-0.2cm}Precip. first 2 months of season&---&---&$-0.003$ $(0.040)^{}$\\
  \\
         \vspace{-0.2cm}Dry spell - max length&---&---&$-0.050$ $(0.031)^{}$\\
  \\
        \vspace{-0.2cm}Dry spells $>9$ days&---&---&$0.018$ $(0.032)^{}$\\
  \\
          \vspace{-0.2cm}Max precipitation&---&---&$-0.008$ $(0.064)^{}$\\
  \\
          \vspace{-0.2cm}Degree days ($10-30$\degree C)&---&---&$-0.016$ $(0.092)^{}$\\
  \\
          \vspace{-0.2cm}Heat wave days ($>35$\degree C)&---&---&$0.032$ $(0.039)^{}$\\
  \\
          \vspace{-0.2cm}Max temperature&---&---&$0.278$ $(0.136)^{*}$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \vspace{-0.1cm} \\ 
  \hline
    \vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{AIC:}}&$2114.98$&$2144.88$&$2118.15$\\

\hline
\vspace{-0.2cm}
\end{tabular} 
\end{small}
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets, \hspace{0.05cm}$1256$ observations
        \begin{adjustwidth}{1cm}{} 
    \item \hspace{0.45cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
     \end{adjustwidth}
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\linespread{1}

{\centering
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(2,1) errors}}
%AmArE2100, AmArE21
\label{ARMA21} 
\centering
\begin{small}
\begin{tabular}{lccc} 
\hline \vspace{-0.2cm} \\

  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}  &\multicolumn{1}{c}{\textit{Model 1}} &\multicolumn{1}{c}{\textit{Model 2}} &\multicolumn{1}{c}{\textit{Model 3}}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.299$ $(0.064)^{***}$&$0.240$ $(0.064)^{***}$&$0.270$ $(0.074)^{***}$\\
  \\
\vspace{-0.2cm}Precipitation total&$0.273$ $(0.042)^{***}$&$0.159$ $(0.051)^{**}$&$0.219$ $(0.117)^{\bullet}$\\
  \\
  \vspace{-0.2cm}Precipitation total sq.&$-0.066$ $(0.026)^{*}$&$-0.079$ $(0.028)^{**}$&$-0.094$ $(0.037)^{*}$\\
  \\
  \vspace{-0.2cm}Temperature - average&$-0.177$ $(0.061)^{**}$&$-0.191$ $(0.062)^{**}$&$-0.380$ $(0.133)^{**}$\\
  \\
    \vspace{-0.2cm}Precip. $\times$ temperature&---&$-0.135$ $(0.037)^{**}$&$-0.101$ $(0.049)^{*}$\\
  \\
      \vspace{-0.2cm}Prec. c. of variation&---&$-0.139$ $(0.040)^{***}$&$-0.091$ $(0.070)^{}$\\
  \\
        \vspace{-0.2cm}Temp. std. dev.&---&$0.038$ $(0.024)^{}$&$0.038$ $(0.026)^{}$\\
  \\
          \vspace{-0.2cm}Precip. first 2 months of season&---&---&$-0.009$ $(0.037)^{}$\\
  \\
         \vspace{-0.2cm}Dry spell - max length&---&---&$-0.045$ $(0.030)^{}$\\
  \\
        \vspace{-0.2cm}Dry spells $>9$ days&---&---&$0.008$ $(0.031)^{}$\\
  \\
          \vspace{-0.2cm}Max precipitation&---&---&$-0.035$ $(0.060)^{}$\\
  \\
          \vspace{-0.2cm}Degree days ($10-30$\degree C)&---&---&$-0.015$ $(0.088)^{}$\\
  \\
          \vspace{-0.2cm}Heat wave days ($>35$\degree C)&---&---&$0.040$ $(0.037)^{}$\\
  \\
          \vspace{-0.2cm}Max temperature&---&---&$0.207$ $(0.123)^{\bullet}$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \vspace{-0.1cm} \\ 
  \hline
  \vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{AIC:}}&$2064.54$&$2064.99$&$2099.90$\\

\hline
\vspace{-0.2cm}
\end{tabular} 
\end{small}
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets, \hspace{0.05cm}$1256$ observations
        \begin{adjustwidth}{1cm}{} 
    \item \hspace{0.45cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
     \end{adjustwidth}
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\linespread{1}

### 2018-11-14 writing/draft1/draftMonika5.tex
adding

{\centering
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(0,0) errors}}
% AmBEST00, AmBEST, AmBEST99
\label{Models1} 
\centering
\begin{small}
\begin{tabular}{lccc} 
\hline \vspace{-0.2cm} \\

\vspace{-0.2cm} \\

  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}  &\multicolumn{1}{c}{\textit{Model 1}} &\multicolumn{1}{c}{\textit{Model 2}} &\multicolumn{1}{c}{\textit{Model 3}}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.298$ $(0.066)^{***}$&$0.256$ $(0.061)^{***}$&$0.243$ $(0.076)^{**}$\\
  \\
\vspace{-0.2cm}Precipitation total&$0.289$ $(0.045)^{***}$&$0.131$ $(0.046)^{**}$&$0.137$ $(0.125)^{}$\\
  \\
  \vspace{-0.2cm}Precipitation total sq.&$-0.071$ $(0.028)^{*}$&$-0.075$ $(0.026)^{**}$&$-0.073$ $(0.039)^{\bullet}$\\
  \\
  \vspace{-0.2cm}Temperature - average&$-0.202$ $(0.062)^{**}$&$-0.188$ $(0.058)^{**}$&$-0.464$ $(0.144)^{**}$\\
  \\
    \vspace{-0.2cm}Precip. $\times$ temperature&---&$-0.135$ $(0.037)^{***}$&$-0.108$ $(0.051)^{*}$\\
  \\
      \vspace{-0.2cm}Prec. c. of variation&---&$-0.198$ $(0.035)^{***}$&$-0.181$ $(0.075)^{*}$\\
  \\
        \vspace{-0.2cm}Temp. std. dev.&---&$0.064$ $(0.021)^{**}$&$0.058$ $(0.027)^{*}$\\
  \\
          \vspace{-0.2cm}Precip. first 2 months of season&---&---&$-0.003$ $(0.040)^{}$\\
  \\
         \vspace{-0.2cm}Dry spell - max length&---&---&$-0.050$ $(0.031)^{}$\\
  \\
        \vspace{-0.2cm}Dry spells $>9$ days&---&---&$0.018$ $(0.032)^{}$\\
  \\
          \vspace{-0.2cm}Max precipitation&---&---&$-0.008$ $(0.064)^{}$\\
  \\
          \vspace{-0.2cm}Degree days ($10-30$\degree C)&---&---&$-0.016$ $(0.092)^{}$\\
  \\
          \vspace{-0.2cm}Heat wave days ($>35$\degree C)&---&---&$0.032$ $(0.039)^{}$\\
  \\
          \vspace{-0.2cm}Max temperature&---&---&$0.278$ $(0.136)^{*}$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \vspace{-0.1cm} \\ 
  \hline
    \vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{AIC:}}&$2114.98$&$2144.88$&$2118.15$\\

@@

{\centering
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(2,1) errors}}
%AmArE2100, AmArE21
\label{ARMA21} 
\centering
\begin{small}
\begin{tabular}{lccc} 
\hline \vspace{-0.2cm} \\

\vspace{-0.2cm} \\

  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}  &\multicolumn{1}{c}{\textit{Model 1}} &\multicolumn{1}{c}{\textit{Model 2}} &\multicolumn{1}{c}{\textit{Model 3}}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.299$ $(0.064)^{***}$&$0.240$ $(0.064)^{***}$&$0.270$ $(0.074)^{***}$\\
  \\
\vspace{-0.2cm}Precipitation total&$0.273$ $(0.042)^{***}$&$0.159$ $(0.051)^{**}$&$0.219$ $(0.117)^{\bullet}$\\
  \\
  \vspace{-0.2cm}Precipitation total sq.&$-0.066$ $(0.026)^{*}$&$-0.079$ $(0.028)^{**}$&$-0.094$ $(0.037)^{*}$\\
  \\
  \vspace{-0.2cm}Temperature - average&$-0.177$ $(0.061)^{**}$&$-0.191$ $(0.062)^{**}$&$-0.380$ $(0.133)^{**}$\\
  \\
    \vspace{-0.2cm}Precip. $\times$ temperature&---&$-0.135$ $(0.037)^{**}$&$-0.101$ $(0.049)^{*}$\\
  \\
      \vspace{-0.2cm}Prec. c. of variation&---&$-0.139$ $(0.040)^{***}$&$-0.091$ $(0.070)^{}$\\
  \\
        \vspace{-0.2cm}Temp. std. dev.&---&$0.038$ $(0.024)^{}$&$0.038$ $(0.026)^{}$\\
  \\
          \vspace{-0.2cm}Precip. first 2 months of season&---&---&$-0.009$ $(0.037)^{}$\\
  \\
         \vspace{-0.2cm}Dry spell - max length&---&---&$-0.045$ $(0.030)^{}$\\
  \\
        \vspace{-0.2cm}Dry spells $>9$ days&---&---&$0.008$ $(0.031)^{}$\\
  \\
          \vspace{-0.2cm}Max precipitation&---&---&$-0.035$ $(0.060)^{}$\\
  \\
          \vspace{-0.2cm}Degree days ($10-30$\degree C)&---&---&$-0.015$ $(0.088)^{}$\\
  \\
          \vspace{-0.2cm}Heat wave days ($>35$\degree C)&---&---&$0.040$ $(0.037)^{}$\\
  \\
          \vspace{-0.2cm}Max temperature&---&---&$0.207$ $(0.123)^{\bullet}$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \vspace{-0.1cm} \\ 
  \hline
  \vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{AIC:}}&$2064.54$&$2064.99$&$2099.90$\\

>>>>

{\hspace{-1.5cm}
\begin{threeparttable}

\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(0,0) errors}}
% AmBEST00, AmBEST, AmBEST99

\label{Models1}

\begin{small}
\begin{tabular}{lcrcrcr}

\hline \vspace{-0.2cm} \\
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{ }}  &\multicolumn{2}{c}{\textit{Model 1}} &\multicolumn{2}{c}{\textit{Model 2}} &\multicolumn{2}{c}{\textit{Model 3}}\\
    \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}&Estimate&Sum sq.&Estimate&Sum sq.&Estimate&Sum sq.\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.298$ $(0.066)^{***}$&---&$0.256$ $(0.061)^{***}$&---&$0.243$ $(0.076)^{**}$&---\\
  \\
\vspace{-0.2cm}Prec. total&$0.289$ $(0.045)^{***}$&$11.9$&$0.131$ $(0.046)^{**}$&$1.3$&$0.137$ $(0.125)^{}$&$0.3$\\
  \\
  \vspace{-0.2cm}Prec. total sq.&$-0.071$ $(0.028)^{*}$&$1.8$&$-0.075$ $(0.026)^{**}$&$1.5$&$-0.073$ $(0.039)^{\bullet}$&$1.0$\\
  \\
  \vspace{-0.2cm}Temp. - average&$-0.202$ $(0.062)^{**}$&$3.1$&$-0.188$ $(0.058)^{**}$&$2.9$&$-0.464$ $(0.144)^{**}$&$2.9$\\
  \\
    \vspace{-0.2cm}Prec. $\times$ temp.&---&---&$-0.135$ $(0.037)^{***}$&$2.5$&$-0.108$ $(0.051)^{*}$&$1.3$\\
  \\
      \vspace{-0.2cm}Prec. c. of variation&---&---&$-0.198$ $(0.035)^{***}$&$7.6$&$-0.181$ $(0.075)^{*}$&$1.7$\\
  \\
        \vspace{-0.2cm}Temp. std. dev.&---&---&$0.064$ $(0.021)^{**}$&$1.3$&$0.058$ $(0.027)^{*}$&$1.3$\\
  \\
          \vspace{-0.2cm}Prec. first 2 months&---&---&---&---&$-0.003$ $(0.040)^{}$&$0.001$\\
  \\
         \vspace{-0.2cm}Dry spell -length&---&---&---&---&$-0.050$ $(0.031)^{}$&$0.7$\\
  \\
        \vspace{-0.2cm}Dry spells $>9$ days&---&---&---&---&$0.018$ $(0.032)^{}$&$0.09$\\
  \\
          \vspace{-0.2cm}Max precipitation&---&---&---&---&$-0.008$ $(0.064)^{}$&$0.005$\\
  \\
          \vspace{-0.2cm}Degree days&---&---&---&---&$-0.016$ $(0.092)^{}$&$0.009$\\
  \\
          \vspace{-0.2cm}Heat wave d. ($>35$\degree C)&---&---&---&---&$0.032$ $(0.039)^{}$&$0.2$\\
  \\
          \vspace{-0.2cm}Max temperature&---&---&---&---&$0.278$ $(0.136)^{*}$&$1.2$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \vspace{-0.1cm} \\ 
  \hline
    \vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{AIC:}}&$2114.98$&&$2144.88$&&$2118.15$\\

@@

{\hspace{-1.5cm}
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(2,1) errors}}
%AmArE2100, AmArE21
\label{ARMA21} 
\begin{footnotesize}

\begin{tabular}{lcrcrcr}

\hline \vspace{-0.2cm} \\
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{ }}  &\multicolumn{2}{c}{\textit{Model 1}} &\multicolumn{2}{c}{\textit{Model 2}} &\multicolumn{2}{c}{\textit{Model 3}}\\
    \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}&Estimate&F-value&Estimate&F-value&Estimate&F-value\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$0.299$ $(0.064)^{***}$&$13.9$&$0.240$ $(0.064)^{***}$&$14.0$&$0.270$ $(0.074)^{***}$&$13.8$\\
  \\
\vspace{-0.2cm}Prec. total&$0.273$ $(0.042)^{***}$&$63.6$&$0.159$ $(0.051)^{**}$&$64.7$&$0.219$ $(0.117)^{\bullet}$&$65.2$\\
  \\
  \vspace{-0.2cm}Prec. total sq.&$-0.066$ $(0.026)^{*}$&$9.9$&$-0.079$ $(0.028)^{**}$&$10.1$&$-0.094$ $(0.037)^{*}$&$10.2$\\
  \\
  \vspace{-0.2cm}Temp. - average&$-0.177$ $(0.061)^{**}$&$8.4$&$-0.191$ $(0.062)^{**}$&$11.8$&$-0.380$ $(0.133)^{**}$&$8.7$\\
  \\
    \vspace{-0.2cm}Prec. $\times$ temp.&---&---&$-0.135$ $(0.037)^{**}$&$4.6$&$-0.101$ $(0.049)^{*}$&$7.5$\\
  \\
      \vspace{-0.2cm}Prec. c. of var.&---&---&$-0.139$ $(0.040)^{***}$&$11$&$-0.091$ $(0.070)^{}$&$11.1$\\
  \\
        \vspace{-0.2cm}Temp. std. dev.&---&---&$0.038$ $(0.024)^{}$&$2.4$&$0.038$ $(0.026)^{}$&$2.4$\\
  \\
          \vspace{-0.2cm}Prec. 2 months&---&---&---&---&$-0.009$ $(0.037)^{}$&$0.3$\\
  \\
         \vspace{-0.2cm}Dry spell -length&---&---&---&---&$-0.045$ $(0.030)^{}$&$2.2$\\
  \\
        \vspace{-0.2cm}Dry spells $>9$ days&---&---&---&---&$0.008$ $(0.031)^{}$&$0.1$\\
  \\
          \vspace{-0.2cm}Max precipitation&---&---&---&---&$-0.035$ $(0.060)^{}$&$0.2$\\
  \\
          \vspace{-0.2cm}Degree days&---&---&---&---&$-0.015$ $(0.088)^{}$&$0.6$\\
  \\
          \vspace{-0.2cm}Heat wave d.&---&---&---&---&$0.040$ $(0.037)^{}$&$3.1$\\
  \\
          \vspace{-0.2cm}Max temperature&---&---&---&---&$0.207$ $(0.123)^{\bullet}$&$2.8$\\
  \\
  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
  \vspace{-0.1cm} \\ 
  \hline
  \vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{AIC:}}&$2064.54$&&$2064.99$&&$2099.90$\\

\hline
\vspace{-0.2cm}
\end{tabular} 
\end{footnotesize}
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets, \hspace{0.05cm}$1256$ observations
        \begin{adjustwidth}{1cm}{} 
    \item \hspace{0.45cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
     \end{adjustwidth}
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\linespread{1}
